%!TEX program = lualatex

\documentclass{modernthesis}
\modernthesissetup{
    title={Example Document using the Modernthesis Template},
    author={Claudio Mattera},
    email={fake@email.com},
    linkedin={linkedin},
    orcid={0000-0002-3801-5617},
    googlescholar={Rw6VmLsAAAAJ},
    researcherid={P-3517-2018},
    year=2019,
    month=2,
    mainauthorpublications={
        doi:10.1109/BigDataService.2017.48,
        doi:10.1093/ijlct/cty019,
        doi:10.1109/ISAECT.2018.8618755,
        doi:10.3390/s18113931,
        doi:10.3390/en12030468,
        Mattera2019b,
    },
    coauthorpublications={
        doi:10.1016/j.egypro.2017.09.625,
        doi:10.1016/j.enbuild.2018.02.005,
        doi:10.1145/3277868.3277875,
        Jradi2019,
        Arendt2019,
    },
    showprinter,
    acronyms,
    glossary,
    cfivepaper,
    separatebibliography,
    highlightannotatedauthors,
    highlightpubstate,
    rotatesidewaysfloats,
    showopenaccess,
}

\input{preamble}


% Put glossary definitions in glossary.tex
\loadglsentries[main]{glossary}

% Put glossary definitions in acronyms.tex
\loadglsentries[\acronymtype]{acronyms}

% Load bibliography
\addbibresource{bibliography.bib}




\begin{document}

\frontmatter

\include{front-back-matter/title}
\include{front-back-matter/abstract}
\include{front-back-matter/publications}
\include{front-back-matter/acknowledgments}
\include{front-back-matter/contents}
\include{front-back-matter/structure}

\cleardoublepage

\mainmatter

\part{Background}
\label{part:background}

This \lcnamecref{part:background} serves as a general introduction to the work carried out during the \phd project.
\Cref{chap:introduction} introduces the context of this thesis and presents the motivation, the research questions and the methodology.
The current state of the art of the field is reviewed in \cref{chap:state-of-art}, where its gap is highlighted, and the contribution of the thesis is presented.

\include{chapters/introduction}
\include{chapters/state-of-art}

\part{Publications}
\label{part:publications}

In this \lcnamecref{part:publications}, are reported, one per \lcnamecref{chap:publications:first-publication}, the following publications.

\printbibliography[
    segment=1,
    heading=none,
]

Figures and tables were minimally edited to fit the layout of this thesis, and they are otherwise identical to the ones in aforementioned publications.
Text was copied verbatim, except for bibliography reference numbers and styles which are kept uniform for the entire thesis, and for minor spelling adaptations and corrections.

\iftoggle{separatebibliography}{
A local bibliography is reported at the end of each \lcnamecref{chap:publications:first-publication}, listing all references cited in the corresponding publication.
All references are also repeated in the global bibliography at the end of this thesis, on page~\pageref{chap:bibliography}.
}{}

\include{publications/first-publication/publication}
\include{publications/second-publication/publication}
\include{publications/third-publication/publication}

\part{Conclusions}
\label{part:conclusions}

This \lcnamecref{part:conclusions} concludes the thesis.
In \cref{chap:future-research}, future research directions are suggested in the context of the thesis.
The findings of the thesis are summarized and elaborated in \cref{chap:conclusions}.

\include{chapters/future-research}
\include{chapters/conclusions}

\appendix

\backmatter

% Printing the entire bibliography, even entries that were not cited in
% the thesis.
%\nocite{*}

\addchap{Bibliography}\label{chap:bibliography}

\AtNextBibliography{\restorebibmacro{pageref}}
\printbibliography[
    heading=none,
    prenote=openaccess,
]

% \glsaddallunused
\end{document}
